Bird beak's elaboration and innovation

### 2022-04-27 Analysis/04-Figure1_with_ellipse_scalling_and_8D_histograms.Rmd
updated figure 4 with thermos

    ## Empty plot
    par(bty = "n")
    plot(NULL, xlim = c(-0.5,1.5), ylim = c(0,lim_up), xaxt = "n", yaxt = "n", xlab = "", ylab = "")

@@

    ## Plot the elaboration/exploration
    par(bty = "n", mar = c(2, 1, 1, 1)+0.1)
    plot.one.proj.rej(results$super_results_between, name.col, x = TRUE, y = FALSE)
}

>>>>

    ## Empty plot
    par(bty = "o")
    plot(NULL, xlim = c(-0.5,1.5), ylim = c(0,lim_up), xaxt = "n", yaxt = "n", xlab = "", ylab = "")

@@

    ## Plot the elaboration/exploration
    par(mar = c(2, 1, 1, 1)+0.1)
    plot.one.proj.rej(results$super_results_between, name.col, x = TRUE, y = FALSE)
}
